Astropy - New software standards for a growing community

### 2017-09-20 main.tex
Update on Overleaf.

\subsection{Convolution}
Astropy implements `normalized convolution' \citep[e.g.][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.   In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.  As of v2.0, the two methods are consistent and include a suite of consistency checks.

@@

\section{Infrastructure for affiliated packages}
\subsubsection{Package template}
bsipocz may write this up tif there is no other takers
\subsection{Continuous integration helpers}
bsipocz should write this up
\subsection{sphinx extensions}
probably Tom R should write this up
\section{State of the Ecosystem}

>>>>

\subsection{Convolution}
Astropy implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.   In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.  As of v2.0, the two methods are consistent and include a suite of consistency checks.

@@

\section{Infrastructure for affiliated packages}
\subsubsection{Package template}
bsipocz may write this up if there is no other takers
\subsection{Continuous integration helpers}
bsipocz should write this up
\subsection{sphinx extensions}
probably Tom R should write this up
\section{State of the Ecosystem}
